### 2020-06-29 Report/aws_325ghz_study.tex
Version submitted June 26.

\section*{Summary}
%
The main objective of this study is to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
mission. In this study, we investigate the possibility to use some 325\,GHz
channels instead.

On basis of the relative humidity (RH) weighting functions of 183\,GHz, three specifications for 325\,GHz channels were suggested. A channel specific simple regression was tested to estimate and correct the impact of hydrometeors in 183\,GHz channel.
The advantage of this approach is that for each 183\,GHz the cloud adjustment
can be quantified simply through a polynomial fit between the the cloud impact
in 183\,GHz channel of concern and brightness temperature differences between
183\,GHz and 325\,GHz. A similar regression scheme based on 229\,GHz was also
examined, but gave poor results. One drawback of the simple correction scheme
is it's channel specific approach, which cannot benefit from the other 325\,GHz
channels available. In order to effectively use information from all 325\,GHz
channels, we suggested a machine learning based approach for cloud correction.
We used QRNN (Quantile Regression Neural Network) to correct the cloud
impact in each 183\,GHz channel using measurements from all available channels
of 325\,GHz. All three options of 325\,GHz were evaluated, and the performance
was comparable. For some channels, interestingly, the spread of errors was
narrower than the noise of the target 183\,GHz channel. Another advantage of
using QRNN is that the cloud free values are predicted at different quantile
levels, which helps in quantifying the case-specific uncertainty estimate. A
similar QRNN model with 229\,GHz gave poor results. No critical dependency to
the 325\,GHz receiver noise temperature was observed.

This study shows that combining measurements from 325\,GHz can provide a better
cloud correction performance than 229\,GHz, and also with minimal rejection of
data. The clear-sky predictions have error distributions which are symmetric
with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
utilise the ``clear-sky'' data can greatly benefit from it. Also, in data
assimilation systems, the case-specific uncertainty allows an effective
selection of weights, thus significantly improving the impact of measurements.
Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is
that NWP systems, which are not yet prepared for 325 GHz, could still benefit
from the data early on.

@@

With 325\,GHz as a better option confirmed, the next step is to establish
requirements for these channels. The study considered this question to some
extent. The cloud correction simulations gave no clear constraints on the
requirements, while the DoF analysis at least gave some indications. By
comparison to the NE$\Delta$T requirements for ICI and DoF values derived, it
is suggested to set threshold, target and breakthrough for the 325\,GHz
receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
number, position and widths of channels, the differences between considered
options are relatively small and at this point, it seems reasonable to let
technical considerations guide the basic selection between having three or four
channels. Later, when the technical constraints (such as the IF range
available) are better known an updated assessment should be performed to set
the final channel values.

\vspace{10mm}
\setcounter{tocdepth}{1} 
\tableofcontents

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{DoF.png}
	\caption{ The ratio of $\Lambda/S_\Lambda$ with respect to the eigenvalue
      index for clear-sky cases. The black dotted line represents the level
      where the ratio is unity. }
	\label{fig:DoF:clear:1200K}
\end{figure}

@@

The DoF values should not be interpreted to strongly. There appears to be some
``noise'' in the DoF, especially for higher noise. For example, in
Table~\ref{tab:DoF:all} all the options have fairly similar DoF for
$T_r=1800$\,K while for $T_r=2400$\,K there are considerable differences. This
shift when going $T_r=2400$\,K is not observed in the two other tables. Having
this in mind, it seems that options three b and c give very similar DoF. If
something, option three-c seems slightly better. The four channel option
obtains somewhat lower DoF than the three channel ones.

@@

The results indicate that a broader IF range should give slightly better performance. If a broader IF range is feasible, the position and width of all channels should be revised, but this is out of the scope of this study, and anyhow hardly motivated before it is known more exactly to what extent the IF range can be extended.

@@

\subsubsection{Channel specifications}
%
We formed three 325\,GHz channel options. All three options were
considered first in the QRNN part as it is difficult to maintain the full
information of all channels in a simple regression based scheme. None of the
three options gave consistently best results, and it is not possible to give a
clear recommendation. For this reason we did not see any value in testing
further options in this part.

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. The option three-a risks to be affected by interference of the downlink
and in the options three-b and c there is a high ratio between bandwidth and centre IF of AWS-42. The latter aspect also makes it hard to extend options three-b and c, if it would turn out that the IF range can be extended. A brief analysis showed that a broader IF range gives some increase in DoF, that potentially could improve the merit of the four channel option.

@@

It is demonstrated that the 325\,GHz channels are capable of providing a more
accurate cloud correction for 183\,GHz than the 229 \,GHz channel. The simple
regression based approach evaluated is channel specific, and involves the
325\,GHz channel one at a time. In the second correction approach based on
machine learning, QRNN is used to predict the clear-sky noise-free values
throughout using all 325\,GHz in parallel. This seems to be a very useful
approach. The QRNN predictions result in error distributions with low skewness
and widths. In some cases, the prediction uncertainty is even lower than the
noise of the 183\,GHz channel targeted. This approach should be ideal for
making use of AWS in assimilation systems of clear-sky type.

>>>>

\section*{Summary}
%
The main objective of this study was to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it had been shown that a channel at 229\,GHz can
be used for this cloud filtering and a 229\,GHz channel forms a part of the
MicroWave Sounder (MWS). In this study, we investigate the possibility to use
some 325\,GHz channels instead, more in line with the Ice Cloud Imager (ICI).

On basis of the relative humidity (RH) weighting functions of 183\,GHz, three
reference specifications for 325\,GHz channels were suggested. A channel
specific simple regression was tested to estimate and correct the impact of
hydrometeors in 183\,GHz channel. The advantage of this approach is that for
each 183\,GHz the cloud adjustment can be quantified simply through a
polynomial fit between the the cloud impact in 183\,GHz channel of concern and
brightness temperature differences between 183\,GHz and 325\,GHz. A similar
regression scheme based on 229\,GHz was also examined, but gave poor results.
One drawback of the simple correction scheme is it's channel specific approach,
which cannot benefit from the other 325\,GHz channels available. In order to
effectively use information from all 325\,GHz channels, we suggested a machine
learning based approach for cloud correction. We used QRNN (Quantile Regression
Neural Network) to correct the cloud impact in each 183\,GHz channel using
measurements from all available channels of 325\,GHz. All three options of
325\,GHz were evaluated, and the performance was comparable. For some channels,
interestingly, the spread of errors was narrower than the noise of the target
183\,GHz channel. Another advantage of using QRNN is that the cloud free values
are predicted at different quantile levels, which helps in quantifying the
case-specific uncertainty estimate. A similar QRNN model with 229\,GHz gave
poor results. No critical dependency to the 325\,GHz receiver noise temperature
was observed.

This study shows that combining measurements from 325\,GHz can provide a better
cloud correction performance than 229\,GHz, and also with minimal rejection of
data. The clear-sky predictions have error distributions which are symmetric
with low bias and spread. Therefore, the NWP and standalone 1DVAR models that
utilise ``clear-sky'' data can greatly benefit from it. Also, in data
assimilation systems, the case-specific uncertainty allows an effective
selection of weights, thus significantly improving the impact of measurements.
Another advantage of combining 183\,GHz and 325\,GHz for cloud correction is
that NWP systems, which are not yet prepared for 325 GHz, could still benefit
from the data early on.

@@

With 325\,GHz as a better option confirmed, the next step is to establish
requirements for these channels. The study considered this question to some
extent. The cloud correction simulations gave no clear constraints on the
requirements, while the DoF analysis gave some indications. By
comparison to the NE$\Delta$T requirements for ICI and DoF values derived, it
is suggested to set threshold, target and breakthrough for the 325\,GHz
receiver noise temperature to 2400, 1800 and 1200\,K, respectively. Regarding
number, position and widths of channels, the differences between considered
options are relatively small and at this point, it seems reasonable to let
technical considerations guide the basic selection between having three or four
channels. Later, when the technical constraints (such as the IF range
available) are better known an updated assessment should be performed to set
the final channel values.

\vspace{20mm}
\setcounter{tocdepth}{1} 
\tableofcontents

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=80mm]{DoF.png}
	\caption{ The ratio of the diagonal elements of $\Lambda/S_\Lambda$ with
      respect to the eigenvalue index for clear-sky cases. The black dashed
      line represents the level where the ratio is unity. The crossing between
      the coloured lines and the dashed line gives the DoF value reported.}
	\label{fig:DoF:clear:1200K}
\end{figure}

@@

The DoF values should not be interpreted to strongly. There appears to be some
``noise'' in the DoF, especially for higher noise. For example, in
Table~\ref{tab:DoF:all} all the options have fairly similar DoF for
$T_r=1800$\,K while for $T_r=2400$\,K there are considerable differences. This
shift when going $T_r=2400$\,K is not observed in the two other tables. Having
this in mind, it seems that options three b and c give in overall similar DoF. If
something, option three-c appears slightly better. The four channel option
obtains somewhat lower DoF than the three channel ones.

@@

The results indicate that a broader IF range should give slightly better
performance. If a broader IF range is feasible, the position and width of all
channels should be revised, but this is out of the scope of this study, and
anyhow hardly motivated before it is known more exactly to what extent the IF
range can be extended. Anyhow, as the three channel options already has a high
ratio between bandwidth and centre IF for AWS-42, it seems difficult to make
full use of an increased IF range for a those options and this is why this test
was made using the four channel option.

@@

\subsubsection{Channel specifications}
%
We formed three reference 325\,GHz channel options. All three options were
considered first in the QRNN part as it is difficult to maintain the full
information of all channels in a simple regression based scheme. None of the
three options gave consistently best results, and it is not possible to give a
clear recommendation. For this reason we did not see any value in testing
further options in this part.

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. The option three-a risks to be affected by interference of the
downlink and in the options three-b and c there is a high ratio between
bandwidth and centre IF of AWS-42. .A brief analysis showed that a broader IF
range gives some increase in DoF, that at least could improve the merit of the
four channel option.

@@

It is demonstrated that the 325\,GHz channels are capable of providing a more
accurate overall cloud correction for 183\,GHz than a 229 \,GHz channel. The simple
regression based approach evaluated is channel specific, and involves the
325\,GHz channel one at a time. In the second correction approach based on
machine learning, QRNN is used to predict the clear-sky noise-free values
throughout using all 325\,GHz in parallel. This seems to be a very useful
approach. The QRNN predictions result in error distributions with low skewness
and widths. In some cases, the prediction uncertainty is even lower than the
noise of the 183\,GHz channel targeted. This approach should be ideal for
making use of AWS in assimilation and retrieval systems of clear-sky type.
